# Progress Reporting {-}

## Progress Reporting {-}

```{r}
#| label: setup
#| include: false
Sys.setenv(RETICULATE_PYTHON = "C:/Python312/python.exe")
```

```{python}
#| echo: false
#| output: false
import sys
import importlib
from pathlib import Path

sys.path.append(str(Path.cwd().resolve().parent))

import content.python.api_calls_v2 as api_calls_v2

importlib.reload(api_calls_v2)

count_assessment_type = api_calls_v2.count_assessment_type
count_completed_assessments = api_calls_v2.count_completed_assessments

assessed_structures = count_completed_assessments()
habitat_confirmations = count_assessment_type("Habitat confirmation")
```

This WCRP was initiated in 2023. The initial development of the WCRP included portions of the Quesnel, Bowron, and Cariboo watersheds. Several scoping exercises were completed by the planning team to help guide the initial development of the WCRP, including a threats assessment that detailed the extent, severity, and overall threat of all five barrier types in the Bowron, Quesnel, and Cariboo (see Appendix D). Situation analyses were also completed by the planning team to identify factors that contribute to the prevalence of culverts and dams on the landscape (see Appendix E). In 2025, the geographic scope of the WCRP expanded to include portions of the Cottonwood watershed. Since 2023, the passability of `r reticulate::py$assessed_structures` structures has been assessed, and further habitat assessments were completed at `r reticulate::py$habitat_confirmations` of these.  

## Rehabilitated Barriers {-}

No barriers were rehabilitated through the implementation of this WCRP as of May 2026. 

## Annual Progress Report {-}

Since March 2025, the following actions were completed: 
- The WCRP geographic scope was expanded to include the Cottonwood watershed. The national hydro network layer was processed to develop an initial spawning and rearing model for Pacific salmon. Satellite imagery was reviewed to exclude structures that could be visibly verified to be a bridge, not exist, or were cross ditches that did not connect to a stream. 

- LDN fisheries technicians completed assessments of structures in the LDN watersheds. Field results still need to be reviewed and incorporated into the model. 

- CWF provided LDN planning team members with QGIS (free and open-source geographic information system software) technical support and onboarding, as well as training to: 
    complete guided and independent PSCIS and satellite review of modelled-stream crossings in QGIS, 
    fix submissions via CSV, and 
    run a tributary-by-tributary mapping exercise for the Cottonwood and digitize data into QGIS. 

## Priority Barriers {-}

```{r}
#| label: tbl6
#| tbl-cap: 'Table 6: Structures in the LDN watersheds that are confirmed as barriers to fish passage for Pacific salmon with confirmed spawning or rearing habitat upstream, as of May 2026. Habitat gain represents the amount (km) of spawning or rearing habitat upstream of that barrier to the next structure that will be reconnected for Pacific salmon if that barrier is addressed. The number of structures in a set represents the number of structures that must be addressed concurrently to maximize habitat connectivity. Barriers known to be partially passable are indicated by “yes”, with further details provided in the adjacent column.'
#| warning: false
#| echo: false
source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/LDN_priority_barriers.csv", check.names=FALSE)
ft <- flextable(data)

ft <- format_flextable(ft)
ft
```
